Lexical Richness as a Lens: Exploring the Influence of Social Class on Authors' Writings

### 2024-03-16 paper/paper.qmd
figures and tables done

```{r}
#| label: tbl-authors-cttr
#| tbl-cap: "First Ten Rows of Writing's Word Count and Uniques Word Count"
#| echo: false

@@

## Author's average word counts distribution
```{r}
#| label: Authors-Word-Count-Distribution
#| fig-cap: "Word Count Comparison by Authors"
#| echo: false

@@

```{r}
#| label: multi level model
#| fig-cap: " TODO"
#| echo: false
#| warning: false

@@

Here is a better visualization of the model
```{r}
#| label: multi level model distribution
#| fig-cap: "First Ten Rows of Writing's Word Count and Uniques Word Count"
#| echo: false

@@

# Expalin
@sec-result

## Hugh Garners CTTR and Length
```{r}
#| label: fig-trends-in-birth-rate
#| fig-cap: Trend in Birth Rates in US
#| echo: false

## David Herbert Lawrence CTTR and Length
```{r}
#| label: fig-trends-in-birth-rate-in-young-people
#| fig-cap: Trends in Birth Rates by Age Group
#| echo: false

## Nancy Mitford CTTR and Length
```{r}
#| label: fig-birth-rate-comparison-old-and-young
#| fig-cap: Birth Rate between Younger and Older Population
#| echo: false

## Powell Anthony CTTR and Length
```{r}
#| label: fig-change-in-birth-rates-by-state
#| fig-cap: Change in Birth Rates by State, 2004–2008 to 2015–2019
#| echo: false

>>>>

```{r}
#| label: tbl-authors-cttr
#| tbl-cap: First Ten Rows of Writings Word Count and Uniques Word Count
#| echo: false

@@

## Author's average word counts distribution
```{r}
#| label: fig-authors-Word-Count-Distribution
#| fig-cap: Word Count Comparison by Authors
#| echo: false

@@

@sec-result

```{r}
#| label: tbl-author-cttr-dist
#| tbl-cap: Authors CTTR Average and Standard Deviation
#| echo: false

cttr_distribution <- read.csv(here::here("data/analysis_data/cttr_dist.csv"))

cttr_distribution |>
  select(author, average, stddev) |>
  kable(
    col.names = c("Author", "Average", "Standard Deviation"),
    digits = 2
  )

```{r}
#| label: tbl-multi-lev-model
#| tbl-cap: Model Summary of Multi-level and Negative Binomial model
#| echo: false
#| warning: false

@@

Here is a better visualization of the model
```{r}
#| label: fig-multi-lev-model-by-author
#| fig-cap: Distribution of Draws by Authors
#| echo: false

@@

```{r}
#| label: fig-hugh-cttr-vs-wordcount
#| fig-cap: Comparison Between CTTR and Word Count by Authors
#| echo: false

ggplot(cttr_all, aes(x = corrected_type_token_ratio, y = word_count, color = author)) +
  geom_point() +
  labs(x = "CTTR", y = "Word Count") +
  theme(panel.background = element_rect(fill = "white"),
              panel.grid.major = element_line(colour = "grey"),
              plot.title = element_text(color = "black", size = 14, face = "bold"),
              axis.title = element_text(color = "black"))
```
